A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
\ideaCallout outside \subsection bracket (otherwise build will fail)

		\subsection{Informational closure and level identification \ideaCallout{maybe not necessary}}

		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}

>>>>

		\subsection{Informational closure and level identification}\ideaCallout{maybe not necessary}

		\subsection{Biological Creature may try to achieve closure even the environment is not}\ideaCallout{Maybe not necessary}
